### 2018-01-08 submission/supplemental.Rmd
add tables with P-value < 0.05 for genera RR

>>>>

**Table S8: RR of Adenoma in Stool for each Individual Genera with Initial P-Value under 0.05**

```{r supplemental_table8, echo=FALSE, message=FALSE, warning=FALSE}

temp_8 <- read_csv("../data/process/tables/adn_select_genus_RR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_8) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

kable(temp_8, format = "markdown", align = 'c', padding = 2)

**Table S9: RR of Carcinoma in Stool for each Individual Genera with Initial P-Value under 0.05**

```{r supplemental_table9, echo=FALSE, message=FALSE, warning=FALSE}

temp_9 <- read_csv("../data/process/tables/select_genus_RR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_9) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

kable(temp_9, format = "markdown", align = 'c', padding = 2)

**Table S10: RR of Adenoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

```{r supplemental_table10, echo=FALSE, message=FALSE, warning=FALSE}

temp_10 <- read_csv("../data/process/tables/adn_select_genus_RR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_10) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

kable(temp_10, format = "markdown", align = 'c', padding = 2)

**Table S11: RR of Carcinoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

```{r supplemental_table11, echo=FALSE, message=FALSE, warning=FALSE}

temp_11 <- read_csv("../data/process/tables/select_genus_RR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_11) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

kable(temp_11, format = "markdown", align = 'c', padding = 2)
